Supernova Host Galaxies in the Dark Energy Survey: III. Constraining the SN Ia delay time dstribution

### 2020-12-18 draft.tex
Updates from Overleaf

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[DES SN Ia Galactic Rate]{Supernova Host Galaxies in the Dark Energy Survey: III. The Evolving Galactic Rate of Type Ia Supernovae}

@@

@@

\begin{figure*}
    \centering
    \includegraphics{}
    \caption{Caption}
    \label{fig:my_label}
\end{figure*}

@@

The result of our toy model is shown in Fig. \ref{fig:SFHs}

@@

The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the simple equation:
\begin{equation}
    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
\label{eq:rate1}
\end{equation}
where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years. By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Rates of SNe Ia in DES]{Supernova Host Galaxies in the Dark Energy Survey: III. Constraining the SN Ia delay time dstribution}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}}
    \label{fig:SFHs}
\end{figure*}

@@

@@

The result of our toy model is shown in Fig. \ref{fig:SFHs}. Galaxies with high masses at $z=0$ formed the vast majority of their stars in the first few Gyr and are now likely to be passive with old stellar populations, while low-mass galaxies are currently strongly star-forming with a vast majority of young stars. Galaxies with masses around $10^10 \mathrm{M}_{\odot}$ are composed of a mixture of young and older stellar populations.

@@

The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the simple equation:
\begin{equation}
    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
\label{eq:rate1}
\end{equation}
where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years. As described in Section \ref{sec:incompleteness}, the values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ that we observe are underestimates of the true numbers due to observational incompleteness. We thus estimate the intrinsic numbers of SNe and galaxies by multiplying the observed numbers by their respective incompleteness corrections,

\begin{equation}
    N_{\mathrm{SN,intrinsic}} = \eta_{\mathrm{SN}} \cdot N_{\mathrm{SN, obs}}
\end{equation}
and
\begin{equation}
    N_{\mathrm{G,intrinsic}} = \eta_{\mathrm{G}} \cdot N_{\mathrm{G, obs}}
\end{equation}

By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.
